\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage[margin=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}

\title{final try — Final Exam}
\date{}

\begin{document}

\maketitle



\noindent
\textbf{Total points:} 6
\hfill
\textbf{Number of questions:} 6

\vspace{1em}
\hrule
\vspace{1.5em}


\noindent
\textbf{Question 1 (2.00 pts).}~
Which of the following is equivalent to a neural network with a nonlinear output?


\begin{enumerate}[label=\textbf{\Alph*.}]

  \item A linear combination of inputs

  \item A weighted sum of inputs passed through an activation function

  \item A simple threshold value

  \item A random combination of inputs

\end{enumerate}



\vspace{0.5em}


\noindent
\textbf{Question 2 (1.00 pts).}~
Neural networks are able to generalise.


\begin{enumerate}[label=\textbf{\Alph*.}]
  \item True
  \item False
\end{enumerate}



\vspace{0.5em}


\noindent
\textbf{Question 3 (1.00 pts).}~
How would you represent the output for an image of the digit 5 in a classification problem with 10 classes, one for each digit from 0 to 9?


\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.6cm}



\vspace{0.5em}


\noindent
\textbf{Question 4 (1.00 pts).}~
How do the advancements in computer technology from the third generation to the fourth generation impact the user experience and the functionality of computers?


\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.6cm}



\vspace{0.5em}


\noindent
\textbf{Question 5 (1.00 pts).}~
Using the provided relationship curves between TP and Temp at a variety of constant CHL, and the relationship curves between TP, Secchi, and TSS at a constant CHL, evaluate how changes in Total Phosphorus (TP) might impact water transparency or clarity as measured by Secchi disk depth, considering the role of Total Suspended Solids (TSS) and Chlorophyll (CHL).


\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.6cm}



\vspace{0.5em}


\noindent
\textbf{Question 6 (1.00 pts).}~
Compare and contrast the characteristics of supervised and unsupervised learning in data mining, using specific examples from the provided context to support your analysis.


\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.4cm}
\noindent\makebox[\linewidth]{\hrulefill}
\vspace{0.6cm}





\end{document}
